Model for DES Type Ia Supernova Cosmology Analysis

### 2016-05-11 tex/toy.tex
Pause for a moment

The luminosity of SNe~Ia as a function of time and wavelength are described by the SALT2 model and
its relation to absolute magnitude.
The mean luminosity and intrinsic magnitude dispersion for SNe~Ia are
\begin{align}
\ln{L}_{SNIa} & \sim \mathcal{N}(\ln{1}, 0.02) \\
\sigma_{SNIa} & \sim \ln{\mathcal{N}}(\ln{0.1},0.1).
\end{align}
and for the moment we don't worry about priors on the distribution of $\alpha$ and $\beta$.

@@

\subsection{$p(M)$: Priors on the Top-Level Parameters}

@@

\subsection{SNIa~Probability}
Probability an object is SN~Ia
\begin{align}
p_{SNIa} &= \frac{r_{SNIa}}{r_{SNIa}+r_{SNII}} \nonumber \\
p_{SNII}&=1-p_{SNIa}.
\label{prob:eqn}
\end{align}
\subsection{Type}
The type of the object $T$ is drawn from the Bernoulli distribution 
\begin{equation}
T | p_{SNIa} \sim \mathcal{B}(1-p_{SNIa}),
\end{equation}
with the convention that $T=0$ corresponds to SN~Ia.

The type probability appears explicitly in the calculation of the likelihoods.
\begin{align}
P(T_{SNIa} | z=z_j, X) &= p_{SNIa}\\
P(T_{SNII} | z=z_j, X) &= p_{SNII}
\end{align}
\subsection{Observed Type}
The observed type is assumed to be perfect.
\begin{equation}
T_o = T.
\end{equation}

\subsection{Luminosity}
For our model
\begin{equation}
\ln{L} | T, \ln{L}_{T},\sigma_{T} \sim \mathcal{N}\left( \ln{L}_{T},\frac{\ln{10}}{2.5}\sigma_{T}\right).
\end{equation}

@@

\subsection{Counts}
The luminosity distance comes from the physics-theory function
\begin{equation}
d_L = d_L(z; \Omega_M, w0),
\end{equation}
the flux is
\begin{equation}
f = \frac{L}{4\pi d_L^2},
\end{equation}
and expected counts is
\begin{equation}
c_\star = 10^{Z/2.5}f.
\end{equation}
The distribution of counts for all transients is 
\begin{equation}
c_o | c_\star, \sigma_c \sim \mathcal{N}(c_\star, \sigma_c),
\end{equation}
where $\sigma_c$ is the measurement noise.

>>>>

The luminosity of SNe~Ia as a function of time and wavelength are described by the SALT2 model and
its relation to absolute magnitude.
The mean luminosity and intrinsic magnitude dispersion for SNe~Ia are
\begin{align}
\ln{L}_{SNIa} & \sim \mathcal{N}(\ln{1}, 0.02) \\
\sigma_{SNIa} & \sim \ln{\mathcal{N}}(\ln{0.1},0.1).
\end{align}
and for the moment we don't worry about priors on $\alpha$ and $\beta$ or the distributions of $x_1$ and $c$.

@@

\subsection{$p(M_I|M)$: Probabilities of the Intermediary Parameters.}
\begin{itemize}
\item We only have to worry about the type probabilities in the photometric-typing analysis.
The probability an object is SN~Ia is
\begin{align}
p_{SNIa} &= \frac{r_{SNIa}}{r_{SNIa}+r_{SNII}} \nonumber \\
p_{SNII}&=1-p_{SNIa}.
\label{prob:eqn}
\end{align}

The type of the object $\tau$ is drawn from the Bernoulli distribution 
\begin{equation}
\tau | p_{SNIa} \sim \mathcal{B}(1-p_{SNIa}),
\end{equation}
with the convention that $T=0$ corresponds to SN~Ia.

For each SN~Ia the SALT2 parameters are drawn
\begin{equation}
x_1, c | \text{distribution hyperparameters }  \sim TBD.
\end{equation}

\item
The peak luminosity is drawn from
\begin{equation}
\ln{L} | \tau, \ln{L}_{\tau},\sigma_{\tau} \sim \mathcal{N}\left( \ln{L}_{\tau},\frac{\ln{10}}{2.5}\sigma_{\tau}\right).
\end{equation}

\subsection{$p(O| M, M_I)$: Probability of All Possible Observables}
\begin{itemize}
\item The spectroscopic typing is assumed to be perfect
\begin{equation}
T | \tau ~ \delta (T-\tau).
\end{equation}

\item The spectroscopic redshift is also assumed to be perfect
\begin{equation}
z | z_{host} ~ \delta (z-z_{host}).
\end{equation}
\item  The luminosity distance comes from the physics-theory function
\begin{equation}
d_L = d_L(z; \Omega_M, w0),
\end{equation}
the flux is something like
\begin{equation}
f = 10^{-\frac{\alpha x_1 + \beta c}{2.5}}\frac{L}{4\pi d_L^2} SALT2(t-t_0; x_1, c),
\end{equation}
and expected counts is
\begin{equation}
c_\star = 10^{Z/2.5}f.
\end{equation}
The distribution of counts for all transients is 
\begin{equation}
c | c_\star, \sigma_c \sim \mathcal{N}(c_\star, \sigma_c),
\end{equation}
where $\sigma_c$ is the measurement noise.

\subsection{$\epsilon(O, M, M_I)$: Sample Inclusion Efficiency}

@@

\subsection{SNIa~Probability}
\subsection{Observed Type}
The observed type is assumed to be perfect.
\begin{equation}
T_o = T.
\end{equation}

@@

\subsection{Counts}
